\ \\ \LARGE\bf Speculative Evaluation in Particle Swarm Optimization \thanks{Matthew Gardner, Andrew McNabb, and Kevin Seppi are with the Department of Computer Science, Brigham Young University, 3361 TMCB, Provo, UT 84602 (phone: 801-422-8717; email: \{mjg82,a,k\}@cs.byu.edu).}

### 2010-03-30 honors_thesis/journal_paper/paper.tex

To enumerate all of the possible next positions of a particle, one must simply
evaluate the motion equations for all possible combinations of personal best
and neighborhood best updates that a particle could see.  This produces
$2(n+1)$ speculative positions to be evaluated, where $n$ is the number of
neighbors the particle has.  Because a particle is also its own neighbor, one
of the $2(n+1)$ speculative positions can be eliminated, as a particle cannot
be the source of its $\nbest$ update while not updating its $\pbest$.  Thus we
have $2(n+1)-1$, or $2n+1$, evaluations.  Table~\ref{tab:evals} lists all
possible combinations of updates that can be seen by a particle with two
neighbors other than itself, which is the case in all of the topologies we use.
If all of these speculative positions are evaluated in parallel along with the
original, non-speculative position of the particle at time $t-1$, then one of
the speculative positions has to be the correct one, and two iterations have
been evaluated at once.

@@

A particle at iteration $t-1$ that has been moved to iteration $t$, but whose
position has not yet been evaluated, is denoted as $\noeval{\p}_t$.  Once its
position has been evaluated, but it has still not yet received information from
its neighbors, it is denoted as $\nonbest{\p}_t$.  Only when the particle has
updated its neighborhood best is it a complete particle at iteration $t$.  It is
then simply denoted as $\p_t$.

@@

In a centralized, or Master-Slave, parallel PSO algorithm, one machine, the
master, keeps track of all necessary information, and all other machines are
merely used to evaluate the objective function at various positions as directed
by the master~\cite{belal-ijicis04}.  To perform speculative evaluation in such
a scheme, the master generates the positions to evaluate speculatively and
decides which one to accept for each particle.  The outline of the procedure is
given in \alg{centralized}.

\begin{algorithm}
  \caption{Speculative Evaluation in a Centralized PSO}
  \label{alg:centralized}
  \begin{algorithmic}[1]
	\STATE Move all $\p_{t-1}$ to $\noeval{\p}_t$
	\STATE For each $\noeval{\p}_t$, get its neighbors $\noeval{\nset}_t$ and
	  generate $\noeval{\sset}_{t+1}$
	\STATE Evaluate all $\noeval{\p}_t$ and $\noeval{\sset}_{t+1}$ in parallel
	\STATE Update personal best for each $\noeval{\p}_t$ and
	  $\noeval{\s}_{t+1}$, creating $\nonbest{\p}_t$ and $\nonbest{\s}_{t+1}$
	\STATE Update neighborhood best for each $\nonbest{\p}_t$, creating
	  $\pset_t$
	\FORALL{$\p_t$}
	\STATE Pick $\nonbest{\s}_{t+1}$ from $\nonbest{\sset}_{t+1}$ that matches
	  the branch taken by $\p_t$
	\STATE Pass along personal and neighborhood best values obtained by $\p_t$,
	  making $\nonbest{\p}_{t+1}$
	\ENDFOR
	\STATE Update neighborhood best for each $\nonbest{\p}_{t+1}$, creating
	  $\pset_{t+1}$
	\STATE Repeat
  \end{algorithmic}
\end{algorithm}

@@

The master then has the slaves evaluate the particles.  Once all particles,
speculative and original, have been evaluated and the values reported to the
master, the master sorts out which speculative child of each particle was the
correct one.

@@

The parent $\p_t$ must pass its personal best value to the child, as the child
knows only the position that it guessed, not the function value at that
position.  It is possible that both $\p_t$ and $\s_{t+1}$ update their
personal bests, but $\p_t$'s value is better.  For example, suppose that
$\p_{t-1}$ has a personal best value of 3.  $\noeval{\p}_t$ is created, and
$\noeval{\s}_{t+1}$ is moved assuming that $\p_t$ has updated its personal
best with its position at time $t$.  Then both $\noeval{\p}_t$ and
$\noeval{\s}_{t+1}$ are evaluated, with values 1 and 2, respectively.
$\nonbest{\s}_{t+1}$ would think that its current position is its personal
best, as the value it found, 2, is better than its previous personal best
value of 3.  It needs to receive the personal best value from its parent to
know that its personal best position $\pbest$ is actually the position of
$\p_t$, not $\s_{t+1}$.

@@

We ran experiments to compare our speculative PSO algorithm to the standard PSO
algorithm.  At each iteration of the algorithms, we use one processor to
perform one function evaluation for one particle, be it speculative or
non-speculative.  For benchmark functions with very fast evaluations this may
not be the best use of parallelism in PSO.  But for many real-world
applications, the objective function takes on the order of minutes or more to
evaluate; in such cases our choice of framework is reasonable.

@@

To use the same number of processors (and hence evaluations) for each
algorithm, speculative evaluation needs a smaller swarm size than standard PSO.
For each of the topologies we used, a particle has three neighbors including
itself.  As shown in Table~\ref{tab:evals}, this results in $7$ speculative
evaluations per particle.  With one evaluation needed for the original,
non-speculative particle, we have $8p_s$ evaluations for every two iterations,
where $p_s$ is the number of particles in the speculative swarm.  The extra
evaluations done in speculative evaluation would instead be particles in
regular PSO, so we compare swarms of size $p_s$ in speculative evaluation with
swarms of size $8p_s$ in regular PSO.

Where the Complete topology would normally be used, we use a Random topology in
our speculative algorithm, as Complete leads to an explosion of speculative
evaluations.  If speculative evaluation were not being performed, it is
possible that the Complete topology would be used.  However, the Complete
topology also requires a very large amount of interprocessor communication in
parallel PSO, so it is still quite possible that Random would be used even with
standard PSO.  But, to be fair in our comparisons, we compare to the standard
PSO algorithm using both the Random topology with two neighbors and the
Complete topology.  All functions have 20 dimensions, and all results shown are
averages over 20 runs.  We use 240 processors in our experiments, so our
speculative algorithm uses 30 particles and standard PSO uses 240 particles.
For ease of labeling, we call our speculative algorithm SEPSO and standard PSO
just PSO, with the topology following.

@@

Next we look at the function Griewank, defined by the equation $f(\Vec{x}) =
\frac{1}{4000} \sum_{i=1}^D x_i^2 - \Pi_{i=1}^D \cos\left(\frac{x_i}{\sqrt{i}}
\right) + 1$.  It is generally recommended to use the Ring topology when
optimizing the Griewank function, as Complete is prone to premature convergence
on a local optima.  We show results in \fig{basic-griewank1} for swarms of size
30 and 240 using the Ring topology. One can see in the figure that using
speculative evaluation initially outperforms PSO, but gets stuck in a local
optima and is eventually outperformed.

\begin{figure}
  \centering
  \includegraphics[width=.8\columnwidth]{griewank1}
  \caption{Function Griewank with a swarm that uses 240 processors per round of
  evaluations.}
  \label{fig:basic-griewank1}
\end{figure}

\fig{basic-griewank1} is slightly deceptive, however, as with Griewank some of
the runs found the global optimum, 0, while some did not.  A more accurate plot
for this function is one showing what percentage of the runs have found the
global optimum at each iteration.  \fig{basic-griewank2} shows such a plot.  A
swarm of size 30 performing the PSO algorithm gets stuck a little less than
half of the time, while 240 particles provides enough exploration to find the
global optimum every time.  As would be expected, when our speculative
algorithm finds the global optimum, it finds it about twice as fast as regular
PSO---it is just performing regular PSO twice as fast with a smaller swarm
size.

@@

While the idea of speculative evaluation in particle swarm optimization is
intriguing, the results of the previous section show that in many cases it
requires too many extra evaluations to produce competitive results.  On most
functions, the larger swarm size that can be used in regular PSO leads to
better performance than is found by trying to do speculative evaluation.
However, if we keep the idea of speculative evaluation while relaxing the
requirement of exactly reproducing the behavior of the original PSO algorithm,
we see some very impressive results.

@@

Row 1 in Table~\ref{tab:branches} corresponds to the phenomenon commonly called
stagnation in the literature, but only with a single particle.  As an
interesting aside, we found that complete stagnation practically never occurs
in PSO, though frequently large percentages of the swarm are stagnant.
Iterations where the entire swarm is stagnant average less than 2 in 1000
iterations, unless the swarm converges beyond machine precision.  When graphs
of the best function value flat-line, what really has happened is a contraction
of the particles' velocity, not stagnation in the technical sense.

@@

Another possibility is to pick the best child, as described in \sec{pickbest}.
This ignores the fact that the branch might have been wrong; we do not care,
because we just want the child that had the best value, anyway.  In almost all
of the experiments that we ran, it turned out that picking the best child
performed better than keeping the particle back an iteration.

@@

Because we are now only doing two speculative evaluations per particle, with
240 processors we can have a swarm of size 80, instead of the 30 particles in
previous experiments.

@@

When looking at the function Griewank, presented in \fig{griewank-pruned}, we
see different results.  Our intuition about picking the best child is more
correct in this case; while adding 50 more particles to the swarm, Pick Best
with pruning still gets stuck more often than the original Pick Best.  However,
Social Promotion does well in this case, finding the optimum every time and
faster than the original PSO, without the need to increase the number of
processors.

@@

When speculating more than one iteration ahead, the idea of picking the child
that matches the correct branch, and holding back the particle if no child
matches the branch, does not make very much sense, as correct branches can only
be determined for the first iteration.  Thus when speculating more than one
iteration ahead we always pick the child that has the highest value.

The question of which branches to take in this infinite tree is an intriguing
one that we can only begin to explore here.  If the branch corresponding to
stagnation has a 75\% chance of being taken, as in the Random topology with
most functions, we could speculate three iterations ahead on that branch and
still have a 42\% chance of predicting correctly.  However, intuition would say
that perhaps it is better to hope that the particle is productive instead of
stagnant, so a branch where the particle updates its personal best might be
more fruitful to try.  In our experiments we try just one of the countless
possibilities, but that one turns out to work extremely well.  More work is
needed to compare the different branching possibilities on various functions.

@@

With the function Griewank, the premature convergence problems inherent in
picking the best child are exacerbated when speculating several iterations
ahead.  When the algorithm converges, it converges quicker than any other 
method we tried.  However, it also got stuck and failed to find the optimum
more than any other method.  In order for this method to be consistently useful
on functions like Griewank, it seems that more processors are required.  The
results are shown in \fig{griewank-manyiters}.

@@

\subsection{Other possibilities}
\label{sec:other}

One issue remains.  What if we really want a swarm of 50 particles, but we have
230 processors to use?  The methods we have thus far presented do the same
thing for every particle, and thus would require some multiple of 50
processors---we would have 30 extra processors with nothing to do.  It might
very well be the best idea to simply adjust the swarm size slightly, but we
present another method that allows particles to behave differently, some doing
more evaluations than others.

If we use the concept of tokens commonly used in multi-robot stuff (see, for
example, \dots), we can specify a number of tokens available for particles to
use, where each token corresponds to a speculative evaluation.  Whichever
method is used to decide which evaluations to do, they are prioritized so that
particles with only one or two tokens perform the most valuable speculative
evaluations.  Particles that perform well keep their tokens, and particles that
perform poorly send one token (if they have one) to another random particle in
the swarm.

We choose to define ``perform poorly'' as a failure to update the personal best
when the original particle's position is evaluated.  Clearly there are other
possible methods of deciding when to give up tokens, but many of the methods
that sound the best are difficult in distributed environments, like giving
tokens to that particles that most recently found the globally best positions.
The use of a central machine to decide which particles get tokens would help to
facilitate such methods.

There are thus two distinct uses for tokens.  First, they could be used to try
to evenly spread extra evaluations due to an incompatible number of particles
and processors.  In cursory experimentation, we found that this was not a very
effective use of tokens.  In virtually every case we tried, it was better to
simply change the number of particles to match the number of processors, and 
spread the speculative evaluations evenly throughout the swarm.

The other, more compelling reason to use tokens is to intelligently and
dynamically allocate speculative evaluations to particles that are performing
well.  This really only makes sense when speculating several iterations ahead;
after one or two speculative evaluations, the added benefit from also
evaluating the low-probability branches is negligible.  But by intelligently
allocating speculative evaluations, particles that are going in good directions
move faster by speculating farther with extra tokens, while particles that are
not doing as well lose their tokens.  Those particles likely contribute to the
exploration of the algorithm, and when they find good locations, they start
keeping their tokens, switching roles to become productive particles
themselves.  This approach is very similar in concept to other dynamic swarms,
like the TRIBES method proposed by Clerc (cite).

As in the previous section, we can only offer a very preliminary exploration of
the possibilities of using tokens to improve the allocation of speculative
evaluations to particles.  We used a distributed parallel PSO framework, and in
this setting determining which particles are performing the best globally is
difficult without extensive communication.  Thus we only present results for
the one method of token allocation described above.

The only function for which we saw a benefit when using this technique was
Griewank.  As seen in \fig{griewank-token}, using tokens increased the chance
of finding the optimum to 100\%, while still using far fewer iterations than
standard PSO.  We assume that the relatively poor performance of the technique
on other functions is due to the lack of better token allocation.

\begin{figure}
  \centering
  \includegraphics[width=.8\columnwidth]{griewank7}
  \caption{Function Griewank with a swarm that uses 240 processors per round of
  evaluations, comparing token-based allocation with previous results.}
  \label{fig:griewank-token}
\end{figure}

@@

We gave only a very little attention to the possibilities of token-based
allocation of speculative evaluations to particles.  We imagine that the
benefits of intelligently and dynamically deciding which particles get extra
evaluations could produce very good results.  Future work could explore the use
of a centralized allocator for extra processors or ideas in the multi-robot
task allocation literature, such as auctions, to better assign processors to
particles for speculative evaluations.  While such methods involve extra
communication, with long-running function evaluations the extra overhead of
intelligently allocating resources would likely be negligible.

@@

One more issue arises when dealing with dynamic topologies.  With neighbors
changing each iteration, messages that processors pass to their neighbors need
to be sent to the correct neighbors for each iteration.  In centralized
algorithms and in distributed algorithms with several rounds of message passing
(the first method described above), nothing needs to be changed.  However, in
the case where processors reconstruct information about neighboring particles
from messages, those messages need to be sent to the correct neighbors.  A
particle cannot simply send messages to its neighbors' neighbors'
neighbors---it needs to send messages to its iteration $t$ neighbors' iteration
$t+1$ neighbors, and so on.  For every neighbor outward information is sent,
the iteration also needs to be incremented, as information about neighbors'
neighbors is used during iteration $t+1$, and information about neighbors'
neighbors' neighbors is used to reconstruct information about iteration $t+2$.
Also, this method of message passing again requires the use of random seeds if
the topology is random, so that each processor computes the same neighbors for
a particle as all other processors.

>>>>

To enumerate all of the possible next positions of a particle, one must simply
evaluate the motion equations for all possible combinations of personal best
and neighborhood best updates that a particle could see.  This produces
$2(n+1)$ speculative positions to be evaluated, where $n$ is the number of
neighbors the particle has.  Because a particle is also its own neighbor, one
of the $2(n+1)$ speculative positions can be eliminated, as a particle cannot
be the source of its $\nbest$ update while not updating its $\pbest$.  Thus we
have $2(n+1)-1$, or $2n+1$, evaluations.  Table~\ref{tab:evals} lists all
possible combinations of updates that can be seen by a particle with two
neighbors in addition to itself, which is the case in all of the topologies we
use.  If all of these speculative positions are evaluated in parallel along
with the original, non-speculative position of the particle at time $t-1$, then
one of the speculative positions has to be the correct one, and two iterations
have been evaluated at once.

@@

A particle at iteration $t-1$ that has been moved to iteration $t$ using
Equations~\eqref{eq:velupdate}~and~\eqref{eq:posupdate}, but whose position has
not yet been evaluated, is denoted as $\noeval{\p}_t$.  Once its position has
been evaluated, but it has still not yet received information from its
neighbors, it is denoted as $\nonbest{\p}_t$.  Only when the particle has
updated its neighborhood best is it a complete particle at iteration $t$.  It
is then simply denoted as $\p_t$.

@@

In a centralized, or Master-Slave, parallel PSO algorithm, one machine, the
master, keeps track of all necessary information, and all other machines are
merely used to evaluate the objective function at various positions as directed
by the master~\cite{belal-ijicis04}.  To perform speculative evaluation in such
an architecture, the master generates the positions to evaluate speculatively
and decides which one to accept for each particle.  The outline of the
procedure is given in \alg{centralized}.

\begin{algorithm}
  \caption{Speculative Evaluation in a Centralized PSO}
  \label{alg:centralized}
  \begin{algorithmic}[1]
	\STATE Move all $\p_{t-1}$ to $\noeval{\p}_t$ using
	  Equations~\eqref{eq:velupdate}~and~\eqref{eq:posupdate}
	\STATE For each $\noeval{\p}_t$, get its neighbors $\noeval{\nset}_t$ and
	  generate $\noeval{\sset}_{t+1}$
	\STATE Evaluate all $\noeval{\p}_t$ and $\noeval{\sset}_{t+1}$ in parallel
	\STATE Update personal best for each $\noeval{\p}_t$ and
	  $\noeval{\s}_{t+1}$, creating $\nonbest{\p}_t$ and $\nonbest{\s}_{t+1}$
	\STATE Update neighborhood best for each $\nonbest{\p}_t$, creating
	  $\pset_t$
	\FORALL{$\p_t$}
	\STATE Pick $\nonbest{\s}_{t+1}$ from $\nonbest{\sset}_{t+1}$ that matches
	  the branch taken by $\p_t$
	\STATE Pass along personal and neighborhood best values obtained by $\p_t$,
	  making $\nonbest{\p}_{t+1}$
	\ENDFOR
	\STATE Update neighborhood best for each $\nonbest{\p}_{t+1}$, creating
	  $\pset_{t+1}$
	\STATE Repeat from Step 1 until finished
  \end{algorithmic}
\end{algorithm}

@@

The master then has the slaves evaluate the particles.  Once all particles,
speculative and original, have been evaluated and the values reported to the
master, the master determines which speculative child of each particle was the
correct one.

@@

The parent $\p_t$ must pass its personal best value to the child, as the child
knows only the position that it guessed, not the function value at that
position.  It is possible that both $\p_t$ and $\s_{t+1}$ update their personal
bests, but $\p_t$'s value is better.  For example, suppose that $\p_{t-1}$ has
a personal best value of 3, and the we are seeking to minimize the function.
$\noeval{\p}_t$ is created, and $\noeval{\s}_{t+1}$ is moved assuming that
$\p_t$ has updated its personal best with its position at time $t$.  Then both
$\noeval{\p}_t$ and $\noeval{\s}_{t+1}$ are evaluated, with values 1 and 2,
respectively.  $\nonbest{\s}_{t+1}$ would think that its current position is
its personal best, as the value it found, 2, is better than its previous
personal best value of 3.  It needs to receive the personal best value from its
parent to know that its personal best position $\pbest$ is actually the
position of $\p_t$, not $\s_{t+1}$.

@@

We ran experiments to compare our speculative PSO algorithm to the standard PSO
algorithm.  At each iteration of the algorithms, we use one processor to
perform one function evaluation for one particle, be it speculative or
non-speculative.  We acknowledge that for benchmark functions with very fast
evaluations this may not be the best use of parallelism in PSO.  But for many
real-world applications, the objective function takes on the order of minutes
or more to evaluate; in such cases our choice of framework is reasonable.

@@

To use the same number of processors (and hence evaluations) for each
algorithm, speculative evaluation must use a smaller swarm size than standard
PSO.  For each of the topologies we used, a particle has three neighbors
including itself.  As shown in Table~\ref{tab:evals}, this results in $7$
speculative evaluations per particle.  With one evaluation needed for the
original, non-speculative particle, we have $8p_s$ evaluations for every two
iterations, where $p_s$ is the number of particles in the speculative swarm.
The extra evaluations done in speculative evaluation would instead be particles
in regular PSO, so we compare swarms of size $p_s$ in speculative evaluation
with swarms of size $8p_s$ in regular PSO.

Where the Complete topology would normally be used, we use a Random topology in
our speculative algorithm, as Complete leads to an explosion of speculative
evaluations.  If speculative evaluation were not being performed, it is
possible that the Complete topology would be used.  However, the Complete
topology also requires a very large amount of interprocessor communication in
parallel PSO, so it is still quite possible that Random would be used even with
standard PSO.  But, to be fair in our comparisons, we compare to the standard
PSO algorithm using both the Random topology with two neighbors and the
Complete topology.  All functions have 20 dimensions, and all results shown are
averages over 20 runs.  We use 240 processors in our experiments (except where
otherwise noted), so our speculative algorithm uses 30 particles and standard
PSO uses 240 particles.  For ease of labeling, we call our speculative
algorithm SEPSO and standard PSO just PSO, with the topology following.

@@

Next we look at the function Griewank, defined by the equation $f(\Vec{x}) =
\frac{1}{4000} \sum_{i=1}^D x_i^2 - \Pi_{i=1}^D \cos\left(\frac{x_i}{\sqrt{i}}
\right) + 1$.  It is generally recommended to use the Ring topology when
optimizing the Griewank function, as Complete is prone to premature convergence
on a local optimum.  Griewank has a global optimum with a value of 0, and
sometimes the swarm finds the optimum and sometimes it doesn't.  Instead of
showing average function value at each iteration, a more accurate plot for
Griewank shows the percent of runs that have found the global optimum by each
iteration.  We show results in \fig{basic-griewank2} for swarms of size 30 and
240 using the Ring topology.  One can see in the figure that SEPSO algorithm
finds the optimum faster than the original PSO.  However, because the swarm
size is so small, SEPSO gets stuck a little less than half of the time.

@@

While the idea of speculative evaluation in particle swarm optimization is
intriguing, the results of the previous section show that in many cases it
requires too many extra evaluations to produce competitive results.  On most
functions, the larger swarm size that can be used in regular PSO leads to
better performance than is found by trying to do speculative evaluation.
However, if we keep the idea of speculative evaluation while relaxing the
requirement of exactly reproducing the behavior of the original PSO algorithm,
we see some impressive results.

@@

Row 1 in Table~\ref{tab:branches} corresponds to the phenomenon commonly called
stagnation in the literature, but only with a single particle.  As an
interesting aside, we found that complete stagnation (where the entire swarm is
stagnant) practically never occurs in PSO, though frequently large percentages
of the swarm are stagnant.  Iterations where the entire swarm is stagnant
average less than 2 in 1000 iterations, unless the swarm converges beyond
machine precision.  When graphs of the best function value flat-line, what
really has happened is a contraction of the particles' velocity, not stagnation
in the technical sense.

@@

Another possibility is to pick the best child, as described in \sec{pickbest}.
This ignores the fact that the branch might have been wrong; it does not
matter, because we simply accept the child that had the best value.  In almost
all of the experiments that we ran, it turned out that picking the best child
performed better than keeping the particle back an iteration.

@@

Because we are now only doing two speculative evaluations per particle (along
with evaluating the original particle), with 240 processors we can have a swarm
of size 80, instead of the 30 particles in previous experiments.

@@

When looking at the function Griewank, presented in \fig{griewank-pruned}, we
see different results.  Our intuition about picking the best child is more
correct in this case; while adding 50 more particles to the swarm, Pick Best
with pruning still gets stuck more often than the original Pick Best.  However,
Social Promotion does well in this case, finding the optimum every time and
faster than the original PSO.

@@

When speculating more than one iteration ahead, the idea of Social Promotion
cannot feasibly be implemented, as we can only determine correct branches for
the first iteration.  Thus when speculating more than one iteration ahead we
always pick the child that has the highest value.

The question of which branches to take in this infinite tree is an intriguing
one that we can only begin to explore here.  If the branch corresponding to
stagnation has a 75\% chance of being taken, as in the Random topology with
most functions, we could speculate three iterations ahead on that branch and
still have a 42\% chance of predicting correctly.  However, intuition would say
that perhaps it is better to hope that the particle is productive instead of
stagnant, so a branch where the particle updates its personal best might be
more fruitful to try.  In our experiments we try just one of the countless
possibilities, but that one turns out to work very well.  More work is needed
to compare the different branching possibilities on various functions.

@@

With the function Griewank, the premature convergence problems inherent in
picking the best child are exacerbated when speculating several iterations
ahead.  When the algorithm finds the optimum, it finds it quicker than any
other method we tried.  However, it also got stuck and failed to find the
optimum more than any other method.  In order for this method to be
consistently useful on functions like Griewank, it seems that more processors
are required.  The results are shown in \fig{griewank-manyiters}.

@@

@@

Our methods for determining which speculative evaluations to perform were
independent of the particle; all particles performed the same number and type
of evaluations.  Another way to allocate speculative evaluations is to somehow
use the performance of each particle to determine how many and which extra
evaluations it can have.  We imagine that the benefits of intelligently and
dynamically deciding which particles get extra evaluations could produce very
good results.  Future work could explore the use of a centralized allocator for
extra processors or ideas in the multi-robot task allocation literature, such
as auctions, to better assign processors to particles for speculative
evaluations.  While such methods involve extra communication, with long-running
function evaluations the extra overhead of intelligently allocating resources
would likely be negligible.

@@

One more issue arises when dealing with dynamic topologies.  With neighbors
changing each iteration, messages that processors pass to their neighbors need
to be sent to the correct neighbors for each iteration.  A particle cannot
simply send messages to its neighbors' neighbors' neighbors---it needs to send
messages to its iteration $t$ neighbors' iteration $t+1$ neighbors, and so on.
For every neighbor outward information is sent, the iteration also needs to be
incremented, as information about neighbors' neighbors is used during iteration
$t+1$, and information about neighbors' neighbors' neighbors is used to
reconstruct information about iteration $t+2$.  Also, this method of message
passing again requires the use of random seeds if the topology is random, so
that each processor computes the same neighbors for a particle as all other
processors.
